\documentclass[12pt]{article}

\usepackage{titlesec,fontawesome, titling, wrapfig, graphicx}
\usepackage[margin=1in]{geometry}




\titleformat{\section}
{\Large\scshape}%formatting
{}%numbering
{0em}%distance between number and what comes after it
{}[\titlerule]%what should be written in front of the title


\titleformat{\subsection}
{}
{\faAngleDoubleRight \ }
{0em}
{}

\titleformat{\subsubsection}
{}
{}
{3em}
{}


\renewcommand{\maketitle}{
\begin{flushleft}
{\Huge\bfseries
\theauthor}

\vspace{0.27em}

\faPaperPlane\ some.email@gmail.com\\
\faMobilePhone \ +44 444 444 \faLinkedin \ www.linkedin.com\\
\faMapMarker \ Place Address here, Mailbox XXX, State, Country Zip Code\\
\faCalendar \ DOB: December XXth, 2XXX \ \faFemale \ Nationality: Somewhere\\

\end{flushleft}
}

\begin{document}

\title{CV}
\author{Camila Santana}
\maketitle
\section{\faGraduationCap \ Education}
	\subsection{\textbf{Some Senior High School}}
		\subsubsection{August 20XX - June 20XX High School Degree with a GPA of XX}
	\subsection{\textbf{Some University}}
		\subsubsection{August 20XX - Present Currently pursuing my XX year as a Some Degree student.}
\section{\faBriefcase \ Work Experience}
	\subsection{\textbf{University of Somwhere}}
		\subsubsection{Intern for Someone, the Director of Engagement in the Center for Somewhere. \\
		Donec quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu.}
	\subsection{\textbf{Some Institute}}
		\subsubsection{Intern for Someone, the Director of Operations at the Some Institute. \\
		Donec quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu.}
\section{\faCode \ PC Skills}
	\subsection{\textbf{Excel}\ \ \textit{Proficient} \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \faAngleDoubleRight \ \textbf{\LaTeX}\ \ \textit{Proficient}}
	\subsection{\textbf{Python}\ \ \textit{Proficient} \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \faAngleDoubleRight \ \textbf{Microsoft Word}\ \ \textit{Proficient}}
	\subsection{\textbf{C/C++}\ \ \textit{Proficient}\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \faAngleDoubleRight \ \textbf{Powerpoint}\ \ \textit{Proficient}}
\section{\faLanguage \ Languages}
	\subsection{\textbf{Spanish} \ \ \textit{Fluent/Native Speaker} \ \ \ \ \ \faAngleDoubleRight \ \textbf{German} \ \textit{B1.2}}
	\subsection{\textbf{English} \ \ \textit{Fluent/Native Speaker}}
	%\subsection{\textbf{German} \ \textit{Proficient}}


	%\subsection{}
			%\subsubsection{}

\end{document}